### 2018-06-01 source/Ch4-Qweights/paper.tex
reorganised source files
added a lot

@@

\pg
This $\deltu\deltv$ space warrants further discussion: Fig. \ref{plot.psf.uv.dudv} shows, for a given $uv$-track (Fig. \ref{plot.psf.uv.dudv}b), both the corresponding $\deltu\deltv$ domain (Fig. \ref{plot.psf.uv.dudv}c) and point-spread function (Fig. \ref{plot.psf.uv.dudv}a). {The symmetric, negative $uv$-track is treated as a separate track, and thus ignored. This means that we do not fully constrain the noise-PSF (since the covariance matrix of the symmetric track is simply the Hermitian of the first), but we do not seek to constrain it in this section, but rather to show that our results hold.}. We can see that the $\delta u \delta v$-tracks are symmetrical about the origin. The $\delta u \delta v$ space corresponding to a given $uv$-track can thus be most concisely described as a ``filled $uv$-track", with its boundaries defined by the ends of the $uv$-track. The set of $\muelF_{bb'}$, each of which maps one value of the covariance matrix to a fringe in the image-plane, would then characterise a PSF equivalent for the noise distribution, which we refer to as the noise-PSF. In our formalism, the only source of statistical effects in the field are calibration errors and thermal noise. The average variance in all pixels will be given by the diagonal of the covariance matrix and the thermal noise, provided that it truly follows a normal distribution. The only effects which will cause the variance in the image-plane to vary from one pixel to the next are those mapped onto the covariance fringes, i.e. such position-dependent variance fluctuations will be caused by correlated gain errors, which are spurious signal introduced by erroneous gain estimates. Assuming all sources in the field are point-like and distant, then these variance fluctuations will follow a specific distribution, convolved to every source in the field.

@@

\pg
In this section, we show the effect of adaptive quality-based weighting on real data. The dataset used in this section is a single sub-band from an 8-hour LOFAR observation centred on the Extended Groth Strip ($\alpha$=14:19:17.84,$\delta$=52:49:26.49). The observation was performed on August 28th, 2014. The subband includes 8 channels of width 24.414 kHz each, for a total bandwidth ranging from 150.2 to 150.5 MHz. The data have been averaged in time to 1 data point per second. The data was calibrated using Wirtinger calibration \citep[see][and references therein]{2014arXiv1410.8706T,2015MNRAS.449.2668S} and a sky model consisting only of a nearby calibrator source, 3C295. A reference image (a cutout of which is shown in Fig. \ref{image.3c295.goodcal}) was made by calibrating the data according to best practice for LOFAR survey data: 1 calibration solution per 8 seconds and per 4 channels. {The residual data was then corrected by the gain solutions and imaged} using Briggs weighting (robust=0), pixel size of $1.5''$, and deconvolved using the default devoncolution algorithm in DDFacet (Tasse et al., in press).

@@

\begin{figure}[h!]
\centering
\begin{subfigure}{.43\textwidth}
\resizebox{\hsize}{!}{\includegraphics{images/paperfig-goodcal.png}}
\caption{\label{image.3c295.goodcal} Well-calibrated, unweighted restored image of the sky near the centre of the Extended Groth Strip. Used for comparison with the other images. {Units of colourbar are Janskys}. This image was made with data calibrated following best practice (solution intervals of 8 seconds, half the bandwidth). rms=5.87mJy/beam}
\end{subfigure}
\hfill
\begin{subfigure}{.43\textwidth}
\resizebox{\hsize}{!}{\includegraphics{images/paperfig-noweights.png}}
\caption{\label{image.3c295.nocorr} Poorly-calibrated, unweighted restored image of the sky near the centre of the Extended Groth Strip. {Units of colourbar are Janskys}. This image was made with the same data as for Fig. \ref{image.3c295.goodcal}, but averaged in time and calibrated using larger gain solution intervals: 2 minutes and half the bandwidth. rms=86.4mJy/beam}
\end{subfigure}
\hfill
\begin{subfigure}{.43\textwidth}
\resizebox{\hsize}{!}{\includegraphics{images/paperfig-cyrilweights.png}}
\caption{\label{image.3c295.lightcorr} Image made using the same imaging parameters and corrected visibilities as Fig. \ref{image.3c295.nocorr}, using sensitivity-optimal weighting. {Units of colourbar are Janskys}. rms=9.69mJy/beam}
\end{subfigure}
\hfill
\begin{subfigure}{.43\textwidth}
\resizebox{\hsize}{!}{\includegraphics{images/paperfig-fullweights.png}}
\caption{\label{image.3c295.fullcorr} Image made using the same imaging parameters and corrected visibilities as Fig. \ref{image.3c295.nocorr}, using artefact-optimal weighting. {Units of colourbar are Janskys}. rms=15.8mJy/beam}
\end{subfigure}
\caption{\label{image.fourRealImages}Restored images of the centre of the Extended Groth Strip, as seen with an 8-hour observation using the full LOFAR array. Fig. \ref{image.3c295.goodcal} shows an image of the field made with good calibration intervals. Fig. \ref{image.3c295.nocorr} shows an image of the field made with poor calibration intervals. Fig. \ref{image.3c295.lightcorr} shows image made with the same visibilities and imaging parameters, but with the application of the sensitivity-optimal weighting scheme. Fig. \ref{image.3c295.fullcorr}, similarly, differs from Fig \ref{image.3c295.lightcorr} only in that artefact-optimal weights, rather than sensitivity-optimal weights, were used. {The histograms of pixel values in each image have 1000 flux bins ranging from -0.16 Jy to 0.16 Jy. Their ordinates are in log scale.} Pixel size is 1.5'' in all images.}
\end{figure}

@@

\begin{figure}[h!]
\begin{subfigure}{.43\textwidth}
\resizebox{\hsize}{!}{\includegraphics{images/paperfig-goodcal.png}}
\caption{\label{image.3c295.goodcal-2} Well-calibrated, unweighted restored image of the sky near the centre of the Extended Groth Strip. Used for comparison with the other images. Calibration solution intervals used were 8 seconds, half the bandwidth. rms=5.87mJy/beam}
\end{subfigure}
\hfill
\begin{subfigure}{.43\textwidth}
\resizebox{\hsize}{!}{\includegraphics{images/paperfig-antweights.png}}
\caption{\label{image.3c295.antcorr} Image made using the same imaging parameters and corrected visibilities as Fig. \ref{image.3c295.nocorr}, with the application of antenna-based, sensitivity-optimal weighting. Solution interval of 2 minutes, half the bandwidth. rms=6.69mJy/beam}
\end{subfigure}
\caption{\label{image.twoRealImages}Comparison between the well-calibrated image (i.e. the same image as Fig \ref*{image.3c295.goodcal}) and antenna-based sensitivity-optimal weights.  {Units of both colourbars are Jansky}. We see that we recover a very similar image, despite the fact that the data used for the weighted image are averaged by a factor of 8 compared to those used for the unweighted image.}
\end{figure}

@@

\pg
As for performance, the weights used for Fig. \ref*{image.3c295.fullcorr} took 8 hours of computing time on a single core\footnote{Core type: Intel(R) Xeon(R) CPU E5-2660 0 @ 2.20GHz}, working on a 29 GB dataset, which is not particularly large for LOFAR data. Since the problem is massively parallel, this cost can be alleviated. The main bottleneck is likely due to very poor code optimization. As for the weights used for Fig. \ref*{image.3c295.antcorr}, they are computed in 1min6s on the same single core.

>>>>

\chapter{Analysing the Variance of Gain Solutions}\label{chapter.paper}
\minitoc
\input{source/Ch4-Qweights/paperdefs.tex}
\

@@

\pg
This $\deltu\deltv$ space warrants further discussion: Fig. \ref{plot.psf.uv.dudv} shows, for a given $uv$-track (Fig. \ref{plot.psf.uv.dudv}b), both the corresponding $\deltu\deltv$ domain (Fig. \ref{plot.psf.uv.dudv}c) and point-spread function (Fig. \ref{plot.psf.uv.dudv}a). {The symmetric, negative $uv$-track is treated as a separate track, and thus ignored. This means that we do not fully constrain the noise-PSF (since the covariance matrix of the symmetric track is simply the Hermitian of the first), but we do not seek to constrain it in this section, but rather to show that our results hold.} We can see that the $\delta u \delta v$-tracks are symmetrical about the origin. The $\delta u \delta v$ space corresponding to a given $uv$-track can thus be most concisely described as a ``filled $uv$-track", with its boundaries defined by the ends of the $uv$-track. The set of $\muelF_{bb'}$, each of which maps one value of the covariance matrix to a fringe in the image-plane, would then characterise a PSF equivalent for the noise distribution, which we refer to as the noise-PSF. In our formalism, the only sources of statistical effects in the field are calibration errors and thermal noise. The average variance in all pixels will be given by the diagonal of the covariance matrix and the thermal noise, provided that it truly follows a normal distribution. The only effects which will cause the variance in the image-plane to vary from one pixel to the next are those mapped onto the covariance fringes, i.e. such position-dependent variance fluctuations will be caused by correlated gain errors, which are spurious signal introduced by erroneous gain estimates. Assuming all sources in the field are point-like and distant, then these variance fluctuations will follow a specific distribution, convolved to every source in the field.

@@

\pg
In this section, we show the effect of adaptive quality-based weighting on real data. The dataset used in this section is a single sub-band from an 8-hour LOFAR observation centred on the Extended Groth Strip ($\alpha$=14:19:17.84,$\delta$=52:49:26.49). The observation was performed on August 28th, 2014. The subband includes 8 channels of width 24.414 kHz each, for a total bandwidth ranging from 150.2 to 150.4 MHz. The data have been averaged in time to 1 data point per second. The data was calibrated using Wirtinger calibration \citep[see][and references therein]{2014arXiv1410.8706T,2015MNRAS.449.2668S} and a sky model consisting only of a nearby calibrator source, 3C295. A reference image (a cutout of which is shown in Fig. \ref{image.3c295.goodcal}) was made by calibrating the data according to best practice for LOFAR survey data: 1 calibration solution per 8 seconds and per 4 channels. {The residual data was then corrected by the gain solutions and imaged} using Briggs weighting (robust=0), pixel size of $1.5''$, and deconvolved using the default devoncolution algorithm in DDFacet (Tasse et al., in press).

@@

\begin{figure}[h!]
\centering
\begin{subfigure}{.49\textwidth}
\resizebox{\hsize}{!}{\includegraphics{images/paperfig-goodcal.png}}
\caption{\label{image.3c295.goodcal} Well-calibrated, unweighted restored image of the sky near the centre of the Extended Groth Strip. Used for comparison with the other images. {Units of colourbar are Janskys}. This image was made with data calibrated following best practice (solution intervals of 8 seconds, half the bandwidth). rms=5.87mJy/beam}
\end{subfigure}
\hfill
\begin{subfigure}{.49\textwidth}
\resizebox{\hsize}{!}{\includegraphics{images/paperfig-noweights.png}}
\caption{\label{image.3c295.nocorr} Poorly-calibrated, unweighted restored image of the sky near the centre of the Extended Groth Strip. {Units of colourbar are Janskys}. This image was made with the same data as for Fig. \ref{image.3c295.goodcal}, but averaged in time and calibrated using larger gain solution intervals: 2 minutes and half the bandwidth. rms=86.4mJy/beam}
\end{subfigure}
\hfill
\begin{subfigure}{.49\textwidth}
\resizebox{\hsize}{!}{\includegraphics{images/paperfig-cyrilweights.png}}
\caption{\label{image.3c295.lightcorr} Image made using the same imaging parameters and corrected visibilities as Fig. \ref{image.3c295.nocorr}, using sensitivity-optimal weighting. {Units of colourbar are Janskys}. rms=9.69mJy/beam}
\end{subfigure}
\hfill
\begin{subfigure}{.49\textwidth}
\resizebox{\hsize}{!}{\includegraphics{images/paperfig-fullweights.png}}
\caption{\label{image.3c295.fullcorr} Image made using the same imaging parameters and corrected visibilities as Fig. \ref{image.3c295.nocorr}, using artefact-optimal weighting. {Units of colourbar are Janskys}. rms=15.8mJy/beam}
\end{subfigure}
\caption{\label{image.fourRealImages}Restored images of the centre of the Extended Groth Strip, as seen with an 8-hour observation using the full LOFAR array. Fig. \ref{image.3c295.goodcal} shows an image of the field made with good calibration intervals. Fig. \ref{image.3c295.nocorr} shows an image of the field made with poor calibration intervals. Fig. \ref{image.3c295.lightcorr} shows image made with the same visibilities and imaging parameters, but with the application of the sensitivity-optimal weighting scheme. Fig. \ref{image.3c295.fullcorr}, similarly, differs from Fig \ref{image.3c295.lightcorr} only in that artefact-optimal weights, rather than sensitivity-optimal weights, were used. {The histograms of pixel values in each image have 1000 flux bins ranging from -0.16 Jy to 0.16 Jy. Their ordinates are in log scale.} Pixel size is 1.5'' in all images.}
\end{figure}

@@

\begin{figure}[h!]
\begin{subfigure}{.49\textwidth}
\resizebox{\hsize}{!}{\includegraphics{images/paperfig-goodcal.png}}
\caption{\label{image.3c295.goodcal-2} Well-calibrated, unweighted restored image of the sky near the centre of the Extended Groth Strip. Used for comparison with the other images. Calibration solution intervals used were 8 seconds, half the bandwidth. rms=5.87mJy/beam}
\end{subfigure}
\hfill
\begin{subfigure}{.49\textwidth}
\resizebox{\hsize}{!}{\includegraphics{images/paperfig-antweights.png}}
\caption{\label{image.3c295.antcorr} Image made using the same imaging parameters and corrected visibilities as Fig. \ref{image.3c295.nocorr}, with the application of antenna-based, sensitivity-optimal weighting. Solution interval of 2 minutes, half the bandwidth. rms=6.69mJy/beam}
\end{subfigure}
\caption{\label{image.twoRealImages}Comparison between the well-calibrated image (i.e. the same image as Fig \ref*{image.3c295.goodcal}) and antenna-based sensitivity-optimal weights.  {Units of both colourbars are Jansky}. We see that we recover a very similar image, despite the fact that the data used for the weighted image are averaged by a factor of 8 compared to those used for the unweighted image.}
\end{figure}

@@

\pg
As for performance, the weights used for Fig. \ref*{image.3c295.fullcorr} took 8 hours of computing time on a single core\footnote{Core type: Intel(R) Xeon(R) CPU E5-2660 0 @ 2.20GHz}, working on a 29 GB dataset, which is not particularly large for LOFAR data. Since the problem is massively parallel, this cost can be alleviated. The main bottleneck is likely due to very poor code optimization. As for the weights used for Fig. \ref*{image.3c295.antcorr}, they are computed in 1min 6s on the same single core.

### 2018-06-01 source/Ch5-Strategy/strategy.tex
added a lot

\pg
Why, then, use this approach? One reason is, in fact, for the challenge itself. A high-resolution (matching HST resolution), wide-area (multiple degrees wide), high-quality radio survey has \emph{never} been achieved at the time of writing. Many surveys of the radio sky exist, of course, but they tend to combine only two of those three qualities. FIRST\citepads[see][and references therein]{2015ApJ...801...26H}, for example, has achieved tremendous results with a $4''$ resolution, relatively low sensitivity, and no short baselines (thereby missing diffuse emission and extended structure). The VLASS \citepads[see][and references therein]{2013arXiv1312.4602H} will aim to go to a $2.5''$ resolution, medium sensitivity, and few short baselines. There exist many LOFAR sky surveys \citepads[cf.]{2016MNRAS.460.2385W,2017A&A...598A.104S}, but they do not yet make use of international LOFAR, and are thus limited in resolution ($\sim 5''$).%Finally, there will of course be the SKA1-MID survey once the SKA is operational; this survey is expected to provide excellent resolution, sensitivity, and good $uv$-coverage, making it sensitive to diffuse emission as well as point sources.

\pg
In this context, a sky survey made using international LOFAR would be competitive until the SKA-MID survey (and considering it maps the Northern sky rather than the Southern sky, would arguably remain competitive even then). It would also allow LOFAR to fulfill the role of pathfinder in a very literal way, by providing datasets on which algorithms and imaging strategies could be tested before handling SKA data volumes.

\pg
Making a high-resolution full-sky survey using international LOFAR is thus arguably useful in and of itself in terms of interferometric techniques \& instrumentation. What then of its science value? The two most obvious advantages of a good large-sky survey are that they are complete (i.e. they are an accurate sample of the underlying source distribution) while still giving information on rare outlier objects which may happen to lie in the field. This gives scientists access to a wealth of statistics from which to derive more robust estimations of population distributions and associated scientific measures of interest. Furthermore, depending on the quality of a given survey, it might even be able to provide such statistics simultaneously for various different fields of scientific interest.

\pg
Of course, LOFAR is already providing such catalogues - LOTSS \citepads[see][and references therein]{2017A&A...598A.104S}  is only the first of many to come. But these catalogues do not make use of the LOFAR international stations, and thus do not make full use of LOFAR's resolution ($5''$ resolution vs. $0.5''$).  This is so due to the technical challenges introduced by the use of international stations. What would they add to a LOFAR catalogue?

\pg
A high-resolution sky survey has all the advantages listed above with more besides. For AGN science, for example, the higher resolution gives information on smaller scales, which is very relevant to study the turbulent processes in the lobes and the nearby intergalactic medium. We also know that there exist small AGNs: size therefore matters, and resolving these small AGNs (which tend to lie at larger redshifts, hence their smaller angular size) can give extremely salient information on AGN population distributions as a function of the age of the universe. Indeed, for AGN science, the LOFAR international baselines can be the difference between having absolutely no information on size distribution (no resolved AGN) and knowing everything about the AGN size distribution within a given extragalactic field. Finally, resolving sources is very relevant to spectral studies of AGN populations: we know very little about the physics of AGNs at low frequencies. Information on large populations of resolved sources (allowing us to separate compact structure from extended emission) is a prerequisite to begin the statistical work needed to understand these low-frequency AGN physics. As such, the international baselines can bridge a critical gap in the data available to scientists studying AGN science.

@@

\pg
Of course, this does not run the full range of science cases which would benefit from high-resolution maps of large parts of the radio sky. Scientists studying gravitational lensing would benefit greatly from large samples of lensed galaxies. Resolved extragalactic recombination lines (for bright objects) would doubtlessly interest scientists studying galactic evolution. We expect these samples to be a natural byproduct of a large, high-resolution map of the radio sky: if they do not appear, that could indeed be a very interesting scientific result in and of itself.

\pg
More generally, high-resolution surveys provide high-resolution images of everyone's favourite objects and sources. It allows for better optical matching and identification, which is particularly relevant e.g. when needing to associate either a low-z or high-z sources to optical counterpart sources (in the case of the Extended Groth Strip, for example, using the international stations means matching the Hubble Space Telescope's resolution). They therefore provide a much more useful contribution to multi-wavelength datasets. It also improves the image's sensitivity to compact sources embedded in diffuse emission: if the source is better-resolved, then the emission associated with compact sources is more easily separated from emission emitted by its surroundings. This can be of tremendous help in image interpretation. Finally, actually resolving objects allows scientists to have better morphological classification for compact objects, which can be extremely useful e.g. when interested in AGN populations vs star-forming galaxy populations.

@@

\pg
In this section, we briefly describe previous observations of the Extended Groth Strip, an extragalactic field with a rich multi-wavelength coverage described in Table \ref{table.EGS.observation}. It has been long observed as part of the All-Wavelength Extended Groth Strip International Survey collaboration (\citepads{2007ApJ...660L...1D}), which later became part of the CANDELS collaboration (\citepads{2011ApJS..197...35G}). The field is centred at $\alpha=14^h17^m,\delta=+52\deg 30'$, placing it between the tail of Ursa Major and Draco. Its size is $0.7'\times 0.1'$. It has notably been the subject of very deep Hubble Space Telescope observations, which the LOFAR VLBI imaging could attempt to match.

@@

\pg
The first step towards acquiring a deep, high-resolution image of the Extended Groth Strip therefore consists of creating a good, high-resolution model of 3C295 at LOFAR frequencies. Creating this model is one of the key results of this thesis. Starting from a high-resolution VLA model of 3C295, subbands selected across the LOFAR bandwidth are self-calibrated in iteratively greater numbers until a given noise threshold is reached. The flux scale is then boot-strapped based on the results of \citet{arse}. This ensures that 3C295 will be adequately subtracted from all corrected visibilities - including international baselines - and thus that images made using these visibilities will not be polluted by sidelobes from 3C295.

\pg
The work done towards this goal can be found in \cref{section.3c295}, and its result - a high-resolution spectral model of 3C295 - is shown below.

\pg
\textcolor{red}{show key result here}

@@

\pg
Initial direction-independent calibration is done using the same pipeline as for the Lofar Two-metre Sky Survey \citepads[LOTSS,][]{2017A&A...598A.104S}. The killMS-DDF facet-based pipeline \citepads[cf]{2016ApJS..223....2V,2015MNRAS.449.2668S,2017arXiv171202078T} is then used to perform direction-dependent calibration for the entire LOFAR primary beam. This allows us to reach a noise threshold of \textcolor{red}{give noise threshold}.

\begin{figure}[h!]
\centering
\includegraphics[width=0.95\textwidth]{images/{lofar.widefield}.png}
\caption{\label{plot.EGS.lofar.widefield} Full direction-dependent calibrated image of the LOFAR primary beam. Image made without international stations.}
\end{figure}

\pg
This work, and its results, are shown in \cref{section.EGS.lowres}. Note that the AEGIS observations summarised in \cref{table.EGS.observation} do not cover the full LOFAR primary beam. The sources observed at low resolution are therefore matched with SDSS images. Overlays are shown to highlight the wealth of interesting sources, and their optical counterparts, which can be picked up as a byproduct of producing high-resolution maps of the radio sky. We select 12 particularly interesting sources and show the results of source matching for these candidates. Overlays of the same SDSS images with NVSS postage stamps are also shown for comparison. Many of the chosen sources do not lie within the Extended Groth Strip, and are therefore only imaged at low resolution, but follow-up images and observations could be made should the need arise.

@@

\pg
\textcolor{red}{show key result + some discussion here}

>>>>

\pg
Why, then, use this approach? One reason is the challenge itself. A high-resolution (matching HST resolution), wide-area (multiple degrees wide), high-quality\footnote{Reliably artefact-free, with known \& limited decorrelation, etc.} radio survey has \emph{never} been achieved at the time of writing. Many surveys of the radio sky exist, of course, but they tend to combine only two of those three qualities. FIRST \citepads[see][and references therein]{2015ApJ...801...26H}, for example, has achieved tremendous results with a $4''$ resolution, relatively low sensitivity, and no short baselines (thereby missing diffuse emission and extended structure) at $\sim$1.4 GHz. The VLASS \citepads[see][and references therein]{2013arXiv1312.4602H} will aim to go to a $2.5''$ resolution, medium sensitivity, and few short baselines - at frequencies ranging from 2 to 4 GHz. There exist many LOFAR HBA ($\sim$120-240 MHz) sky surveys \citepads[cf.]{2016MNRAS.460.2385W,2017A&A...598A.104S}, but they do not yet make use of international LOFAR, and are thus limited in resolution ($\sim 5''$).%Finally, there will of course be the SKA1-MID survey once the SKA is operational; this survey is expected to provide excellent resolution, sensitivity, and good $uv$-coverage, making it sensitive to diffuse emission as well as point sources.

\pg
In this context, a sky survey made using international LOFAR would be competitive until the SKA-MID survey (and considering it maps the Northern sky rather than the Southern sky, would arguably remain competitive even then). It would also allow LOFAR to fulfill the role of pathfinder in a very literal way, by providing datasets on which algorithms and imaging strategies could be tested before handling SKA data volumes in real-time.

\pg
Making a high-resolution full-sky survey using international LOFAR is thus arguably useful in and of itself in terms of interferometric techniques \& instrumentation. What then of its science value? The two most obvious advantages of a good large-sky survey are that they are complete (i.e. they are an accurate sample of the underlying source distribution, up to the survey's limiting flux)  while still giving information on rare outlier objects which may happen to lie in the field. This gives us access to a wealth of statistics from which to derive more robust estimations of population distributions. %Furthermore, depending on the quality of a given survey, it might even be able to provide such statistics simultaneously for various different fields of scientific interest.

\pg
Of course, LOFAR is already providing such catalogues - LOTSS \citepads[see][and references therein]{2017A&A...598A.104S}  is only the first of many to come. But these catalogues do not make use of the LOFAR international stations, and thus do not make full use of LOFAR's resolution ($5''$ resolution vs. $0.5''$).  This is so due to the technical challenges introduced by the use of international stations, which are due to decorrelation and an already limited signal-to-noise on those very short spatial frequencies.

\pg
What would they add to a LOFAR catalogue? A high-resolution sky survey has all the advantages listed above with more besides. For AGN science, for example, the higher resolution gives information on smaller scales, which is very relevant to study the turbulent processes in the lobes and the nearby intergalactic medium. We also know that there exist small AGNs: size therefore matters, and resolving these small AGNs (which tend to lie at larger redshifts, hence their smaller angular size) can give extremely salient information on AGN population distributions as a function of the age of the universe. Indeed, for AGN science, the LOFAR international baselines can be the difference between having absolutely no information on size distribution (no resolved AGN) and knowing everything about the AGN size distribution within a given extragalactic field. Finally, resolving sources is very relevant to spectral studies of AGN populations: we know very little about the physics of AGNs at low frequencies. Information on large populations of resolved sources (allowing us to separate compact structure from extended emission) is a prerequisite to begin the statistical work needed to understand these low-frequency AGN physics. As such, the international baselines can bridge a critical gap in the data available to peers studying AGN science.

@@

\pg
Of course, this does not run the full range of science cases which would benefit from high-resolution maps of large parts of the radio sky. Colleagues studying gravitational lensing would benefit greatly from large samples of lensed galaxies. Resolved extragalactic recombination lines (for bright objects) would doubtlessly interest peers studying galactic evolution. We expect these samples to be a natural byproduct of a large, high-resolution map of the radio sky: if they do not appear, that could indeed be a very interesting scientific result in and of itself.

\pg
More generally, high-resolution surveys provide high-resolution images of everyone's favourite objects and sources. It allows for better optical matching and identification, which is particularly relevant e.g. when needing to associate either a low-z or high-z sources to optical counterpart sources (in the case of the Extended Groth Strip, for example, using the international stations means matching the Hubble Space Telescope's resolution). They are thus a strong contribution to multi-wavelength datasets. It also improves the image's sensitivity to compact sources embedded in diffuse emission: if the source is better-resolved, then the emission associated with compact sources is more easily separated from emission emitted by its surroundings. This can be of tremendous help in image interpretation. Finally, actually resolving objects allows us to have better morphological classification for compact objects, which can be extremely useful e.g. when interested in AGN populations vs star-forming galaxy populations.

@@

\pg
In this section, we briefly describe previous observations of the Extended Groth Strip (EGS), an extragalactic field with a rich multi-wavelength coverage described in Table \ref{table.EGS.observation}. It has been long observed as part of the All-Wavelength Extended Groth Strip International Survey collaboration (AEGIS, \citetads{2007ApJ...660L...1D}), which later became part of the CANDELS collaboration (\citetads{2011ApJS..197...35G}). The field is centred at $\alpha=14^h17^m,\delta=+52\deg 30'$, placing it between the tail of Ursa Major and Draco. Its size is $0.7'\times 0.1'$. It has notably been the subject of very deep Hubble Space Telescope observations, which the international LOFAR could attempt to match.

@@

\pg
The first step towards acquiring a deep, high-resolution image of the Extended Groth Strip therefore consists of creating a good, high-resolution model of 3C295 at LOFAR frequencies. Creating this model is one of the key results of this thesis. Starting from a high-resolution VLA model of 3C295, subbands selected across the LOFAR bandwidth are self-calibrated in iteratively greater numbers until a given noise threshold is reached. The flux scale is then boot-strapped based on the results of \citet{arse}. This ensures that 3C295 will be adequately subtracted from all corrected visibilities - including international baselines - and thus that images made using these visibilities will not be polluted by sidelobes from 3C295. 
The work done towards this goal is shown in \cref{section.3c295}. %, and its result - a high-resolution spectral model of 3C295 - is shown below.
%
%\pg
%\textcolor{red}{show key result here}

@@

\pg
Initial direction-independent calibration is done using the same pipeline as for the Lofar Two-metre Sky Survey \citepads[LOTSS,][]{2017A&A...598A.104S}. The killMS-DDF facet-based pipeline \citepads[cf]{2015MNRAS.449.2668S,2016ApJS..223....2V,2017arXiv171202078T} is then used to perform direction-dependent calibration for the entire LOFAR primary beam. This allows us to reach a noise threshold of $\sim$233$\mu$Jy.

\begin{figure}[h!]
\centering
\includegraphics[width=0.95\textwidth]{images/{lofar.widefield}.png}
\caption{\label{plot.EGS.lofar.widefield} Full direction-dependent calibrated image of the LOFAR primary beam, centred on the EGS. Image made without international stations.}
\end{figure}

\pg
This work, and its results, are shown in \cref{section.EGS.lowres}. Note that the AEGIS observations summarised in \cref{table.EGS.observation} do not cover the full LOFAR primary beam. The sources observed at low resolution are therefore matched with Sloan Digital Sky Survey (SDSS, \citetads{2000AJ....120.1579Y}) images. Overlays are shown to highlight the wealth of interesting sources, and their optical counterparts, which can be picked up as a byproduct of producing high-resolution maps of the radio sky. We select 12 particularly interesting sources and show the results of source matching for these candidates. Overlays of the same SDSS images with NVSS (NRAO VLA Sky Survey, \citetads{1998AJ....115.1693C}) postage stamps are also shown for comparison. Many of the chosen sources do not lie within the Extended Groth Strip, and are therefore only imaged at low resolution, but follow-up images and observations could be made should the need arise.

@@
